\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-05-05 syscoin_4.0/article.tex
block resize failure model

@@

@@

\begin{eqnarray} \label{eq:eip1559}
b_{k} = b_{k-1} f_{k-1}, \\
f_{k} = \dfrac{1+ \delta_{k}}{c}
\end{eqnarray}
where $\delta_{k} = usage_{k} - target~gas~fee$, and $c = (target)/(basefee~max~change)$.

@@

>>>>

\begin{figure}[h!]
\includegraphics[width=3in]{img/block_failure.png}
\caption{Block resize on failure model (top left) block failure times; (bottom left) block sizings; (top right) block size transfer function; and (bottom right) Kaplain Meier curve; for this simulation we assumed a failure rate of 1\%; once a failure event occurs we estimate the probability of block failure which is fed to the transfer function to determine the block size adjustment} 
\label{fig:block_failure}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=3in]{img/blk_size_simulations.png}
\caption{Block size simulations using the Block Resize on Failure Model as detailed in Figure \ref{fig:block_failure} and Appendix \ref{appendix:block_resize}; the assumed a failure rate was 2\%} 
\label{fig:blk_size_simulations}
\end{figure}

@@

\section{Block Resize on Failure Model}
\label{appendix:block_resize}

This Block Resize on Failure model dynamically adjusts the blocksize based on time to last block failure. If the time interval between failures is short then the probability of failure is high and the size for the next block gets decreased. However, when the time interval between failures is long then the probability of failure is low and the size for the next block size gets increased. This methodology is updated upon each failure, and consists of three main steps which include:
\begin{itemize}
\item Generate a Kaplan Meier estimator based on last N failures
\item Using time interval between last failure get estimated probability of failure using Kaplan Meier estimator
\item Feed the estimated probability of failure into a block size transfer function to get the block size adjustment for the next block
\end{itemize}

The goal of the Kaplan Meier estimator is to estimate the survival function, $S$, defined as:
\begin{equation}
S(t) = Pr(\tau > t),
\end{equation}
where $t$ is time, and  $\tau > 0$ be a random variable. The survivor function for the Kaplan Meier estimator function is given by:
\begin{equation}
\hat{S}(t) = \prod_{i; t_{i} < t} 1- \frac{d_{i}}{n_{i}}
\end{equation}
where $t_{i}$ is a time when at least one black failure happened, $d_{i}$ the number of failures, and $n_{i}$ the blocks that have not failed.

The block size transfer function constructed from the following logit function:
\begin{equation}
y_{tr} = -2*A*\frac{e^{k(x-x_{0})}}{1+e^{k(x-x_{0})}} + A
\end{equation}
where preconfigured parameters ${A,k}$  determine how aggressive the resizing is upon each block failure. These parameters are typically determined aprior based on simulations run on the test net.

@@

\begin{eqnarray} \label{eq:eip1559}
b_{k} = b_{k-1} f_{k}, \\
f_{k} = 1 + \dfrac{\delta_{k}}{c}
\end{eqnarray}
where $\delta_{k} = usage_{k} - target~gas~fee$, and $c = (target)/(basefee~max~change)$.

@@

\bibitem{Moo21}  I. Moore and J. Sidhu. \textit{Stochastic Properties of EIP 1559 Basefees}, 2021. arXiv:2102.02247,  https://arxiv.org/abs/2102.02247
